---
title: "Decision Tree Model"
author: "Gus Vu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
creditcard <- read.csv("C:/Users/gusvu/OneDrive/Desktop/Projects/Creditr Card/creditcard.csv")
```

# Fitting a Decision Tree Model

A decision tree works by classifying an observation into categories in multiple steps, or branches of a tree. The tree will choose a variable and a threshold for that variable. If the observation is over/ under the threshold then the tree decides it is more or less likely to fit in one category. This will make more sense once I plot the tree.

```{r}
library(rpart)
library(rpart.plot)
decisionTree_model <- rpart(Class ~ . , creditcard, method = 'class')
predicted_val <- predict(decisionTree_model, creditcard, type = 'class')
probability <- predict(decisionTree_model, creditcard, type = 'prob')
rpart.plot(decisionTree_model)
```

The nodes on the bottom represent the probabilities of 1 or 0 (fraud or not), given that the predicter variables meet the conditions of that branch. 

```{r}
mean(predicted_val == creditcard$Class)
```
We see that our acuracy is 0.9995471, and our decision tree model is highly effective.